\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

%----------------------------------------------------------------------------------------
% Contact Information
%----------------------------------------------------------------------------------------

\name{Yingzheng "Marko" Ma} % Your name
\address{+1 (424) 386-6571 \\ 
    San Jose, CA, USA \\
    \href{mailto:yingzhengma@gmail.com}{yingzhengma@gmail.com}
} 
\address{\href{https://github.com/marko-yingzheng-ma}{github.com/marko-yingzheng-ma} \\
    \href{https://www.linkedin.com/in/yingzhengmarkma/}{linkedin.com/in/yingzhengmarkma} \\
} 

\begin{document}

%----------------------------------------------------------------------------------------
% Professional Summary
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Summary}

{A self-reliant Full Stack Software Engineer who takes ownership of projects, I am committed to continuous learning and adept at resolving complex problems. With over 5 years of experience in full stack web and mobile development, I am now seeking global opportunities to apply my expertise, having gained valuable experience in the USA.}

\end{rSection}

%----------------------------------------------------------------------------------------
% Work Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\textbf{Full Stack Software Engineer} \hfill Mar 2018 --- Sep 2022 \\
Ford Greenfield Labs, Ford Motor Company \hfill \textit{Palo Alto, CA, USA}
\begin{itemize}
    \item Led the end-to-end architecture, development, and deployment of a highly scalable React Single Page Application (SPA) utilizing Node.js, resulting in a successful MVPs that is now widely adopted by thousands of employees as a go-to project repository.
    \item Led a team of 3 developers in a collaborative effort with the Sync 4 (Ford new infotainment technology) team to test, benchmark, and debug gaming and productivity applications, resulting in the deployment of these applications on over 2,000,000 Ford vehicles.
    \item Designed and implemented a cutting-edge, immersive multiplayer trivia game SPA using React.js and Node.js, integrated within the Sync 4 platform. Streamlined user experience by developing an embedded host app with a QR code scanning feature, enabling seamless participation for riders through a mobile web app. Resulted in increased engagement and enhanced social interaction among users.
    \item Developed an iOS driver application using Swift 4 as part of a First Mile, Last Mile MVP program, resulting in 22,875 fulfilled rides and an impressive average rating of 4.6/5.0.
    \item Introduced and evangelized TDD with CI/CD Jenkins pipelines in dev team of 4, reducing deployment time by 95\% from 1 hour to 5 minutes, and increasing deployment frequency from once per week to an average of 4 times a day. 
    \item Completed 15 diverse Proof Of Concepts (PoC) and Minimum Viable Products (MVP), including full stack Node.js and React.js, iOS (Swift, SwiftUI), and Android (Kotlin) applications, simultaneously managing an average of 2 projects at a time. Recognized as a "top achiever," an honor bestowed upon only 5\% of employees.
\end{itemize}
    
\textbf{Android Engineer Internship} \hfill Sep 2017 --- Dec 2017 \\
SMount Health Tech \hfill \textit{San Jose, CA, USA}
\begin{itemize}
    \item Architected a decentralized mobile health Android application for caregivers to keep track of patients’ health status in real- time while keeping data distributed across all devices.
    \item Retrieved JSON health data from Bluetooth Low Energy (BLE) wearable devices and alert caregivers about patient health condition changes through RabbitMQ messaging broker.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
% Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
  \textbf{Frontend - Web:} & JavaScript, TypeScript, React.js, Redux.js, HTML5/CSS3, UI/UX, Atomic Design \\
    \textbf{Frontend - Mobile:} & Swift, SwiftUI, Objective C, React Native, Java, Kotlin \\
  \textbf{Backend:} & Node.js, Express.js, Python, Java Spring Boot, MySQL, PostgreSQL, MongoDB \\
  \textbf{Testing:} & TDD/BDD, Jest, Mocha, Chai, Quick, Nimble  \\
  \textbf{DevOps:} & GCP, Azure, AWS, CI/CD, Jenkins, Terraform, Docker
\end{tabular}\\

\end{rSection}

%----------------------------------------------------------------------------------------
% Education Section (Shift below Projects if your projects are substantial)
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{Bachelor of Science, Software Engineering}, Drury University, USA \hfill {Aug 2015 --- Aug 2017}
\begin{itemize}
    \item GPA 3.72/4.0
\end{itemize}

\textbf{Bachelor of Science, Computer Science}, The Ohio State University, USA \hfill {Aug 2012 --- May 2015}
\begin{itemize}
    \item GPA 3.5/4.0 (Transferred)
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------

% \begin{rSection}{Projects}

% \textbf{Role}, {Project Name} (\href{https://myproject.com}{myproject.com}) \hfill {MMM YYYY --- MMM YYYY}
% \begin{itemize}
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
% \end{itemize}

% \textbf{Role}, {Project Name} (\href{https://github.com/my-project}{github.com/my-project}) \hfill {MMM YYYY --- MMM YYYY}
% \begin{itemize}
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
% \end{itemize}

% \end{rSection}

%----------------------------------------------------------------------------------------
% Awards
%----------------------------------------------------------------------------------------

\end{document}
